An open reproducible framework for the study of the iterated prisoner's dilemma

### 2015-10-15 paper.tex
Adding some past tournament details to table.

As stated in~\cite{Bendor2015}: ``\textit{few works in social science have had
the general impact of [Axelrod's study of the evolution of cooperation]}''.  In
1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which described
a computer tournament that has been at the origin of a majority of game
theoretic work~\cite{Banks1990, Bendor2015, Boyd1987, Chellapilla1999,
    DavidB1993, Doebeli2005, Ellison1994, Gotts2003, Isaac2008, Kraines1989,
    Lorberbaum1994, Milgrom1982, Molander1985, Murnighan2015, Press2012,
Stephens2002, Stewart2012}. As described in~\cite{Bendor2015} this work has not
only had mathematical impact but has also led to insights in biology (for
example in~\cite{Chellapilla1999}, a real tournament where Blu Jays are the
participants is described) and in particular to the study of evolution.

@@

The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Numerical
values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature. Axelrod's
tournaments (and further implementations of these) are sometimes referred to as
Iterated Prisoner's Dilemma tournaments.

>>>>

As stated in~\cite{Bendor1991}: ``\textit{few works in social science have had
the general impact of [Axelrod's study of the evolution of cooperation]}''.  In
1980, Axelrod wrote two papers:~\cite{Axelrod1980a,Axelrod1980b} which
described a computer tournament that has been at the origin of a majority of
game theoretic work~\cite{Banks1990, Bendor1991, Boyd1987, Chellapilla1999,
DavidB1993, Doebeli2005, Ellison1994, Gotts2003, Hilbe2013, Isaac2008,
Kraines1989, Lee2015, Lorberbaum1994, Milgrom1982, Molander1985, Murnighan2015,
Press2012, Stephens2002, Stewart2012}. As described in~\cite{Bendor1991} this
work has not only had mathematical impact but has also led to insights in
biology (for example in~\cite{Stephens2002}, a real tournament where Blu Jays
are the participants is described) and in particular to the study of evolution.

@@

The game of (\ref{equ:one-shot}) is called the Prisoner's Dilemma. Numerical
values of \((R,S,T,P)=(3,0,5,1)\) are often used in the literature. Axelrod's
tournaments (and further implementations of these) are sometimes referred to as
Iterated Prisoner's Dilemma tournaments, an overview of published tournaments is
given in Table~\ref{tab:tournaments}.

\begin{table}[!hbtp]
    \begin{center}
        \begin{tabular}{ccccc}
            \toprule
            Year     & Reference           & Number of Strategies & Type     & Source Code\\
            \midrule
            1979     & \cite{Axelrod1980a} & 13                   & Standard & Not immediately available\\
            1979     & \cite{Axelrod1980b} & 64                   & Standard & Not immediately available\\
            1991     & \cite{Bendor1991}   & 13                   & Noisy    & Not immediately available\\
            2002     & \cite{Stephens2002} & 16                   & Wildlife & Not applicable\\
            % Is this worth including? If so I think we need more.
            \bottomrule
        \end{tabular}
    \end{center}
    \caption{An overview of published tournaments}\label{tab:tournaments}
\end{table}
